|

### 2020-04-05 paper.Rmd
Added appendix with different numbering

@@

# Appendix

>>>>

# Additional tricks for publishing
* Make your script anonymous
    + Simply put a `<!-- ... -->` around any identifying information, e.g., author names, title footnote etc.
* Counting words
    + Use adobe acrobat (commerical software) to convert your file to a word file. Then open in word and delete all the parts that shouldn't go into the word count. The word count is displayed in the lower right.
    + Use an one of the online services to count your words (search for "pdf word count")

@@

\linespread{1}

::: {#refs}

:::

\appendix
\addtocontents{toc}{\protect\setcounter{tocdepth}{2}}

\renewcommand{\thesection}{A}

\setcounter{page}{1}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\renewcommand{\figurename}{Table}

\setcounter{figure}{0}
\renewcommand\thefigure{A\arabic{figure}}
\renewcommand{\figurename}{Figure}

\clearpage
\pagenumbering{gobble}

\vspace*{7cm}

\begin{center}
\begin{huge}
Online Appendix
\end{huge}
\end{center}
\vspace{3cm}

### 2020-04-05 paper.tex
Added appendix with different numbering

@@

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

>>>>

\hypertarget{additional-tricks-for-publishing}{%
\section{Additional tricks for publishing}\label{additional-tricks-for-publishing}}

\begin{itemize}
\tightlist
\item
  Make your script anonymous

  \begin{itemize}
  \tightlist
  \item
    Simply put a \texttt{\textless{}!-\/-\ ...\ -\/-\textgreater{}} around any identifying information, e.g., author names, title footnote etc.
  \end{itemize}
\item
  Counting words

  \begin{itemize}
  \tightlist
  \item
    Use adobe acrobat (commerical software) to convert your file to a word file. Then open in word and delete all the parts that shouldn't go into the word count. The word count is displayed in the lower right.
  \item
    Use an one of the online services to count your words (search for ``pdf word count'')
  \end{itemize}
\end{itemize}

@@

\hypertarget{references}{%
\section{References}\label{references}}

\linespread{1}

\appendix
\addtocontents{toc}{\protect\setcounter{tocdepth}{2}}

\renewcommand{\thesection}{A}

\setcounter{page}{1}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\renewcommand{\figurename}{Table}

\setcounter{figure}{0}
\renewcommand\thefigure{A\arabic{figure}}
\renewcommand{\figurename}{Figure}

\clearpage
\pagenumbering{gobble}

\vspace*{7cm}

\begin{center}
\begin{huge}
Online Appendix
\end{huge}
\end{center}
\vspace{3cm}

@@
